saycam full dataset -- preprocessing

### 2020-01-24 analysis/analysis_fulldataset.Rmd
separate out analysis scripts for efficiency

## Read in data 
### Load preprocessed and filtered detections
```{r}
load('../data/openpose_detections_filtered.RData') #d_all
load('../data/openpose_detections_filtered_cropped.RData') # d_cropped
```

@@

d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
```

@@

### Plot faces x age x child
```{r}
(faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot hands x age x child
```{r}
(hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)'))
```

@@

### Plot Face AND hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  ylab('Proportion Face AND Hand') + 
  xlab('Age bin')
```

## By location
### Summarize faces vs hands by location
```{r}

@@

# Cropped analysis
## Faces vs hands
### Summary statistics
```{r}
summary_by_age_cropped <- d_cropped %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect)

summary_by_age_cropped_limited <- summary_by_age_cropped %>%
  filter(age_day_bin < 24.1)
```

>>>>

## Read in data 
### Load preprocessed and filtered detections

```{r}
load('../data/openpose_detections_filtered_threekids.RData') #d_all

##
load('../data/openpose_detections_filtered_cropped_allthreekids.RData') # d_cropped
```

@@

d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))

d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
```

@@

### Plot faces x age x child
```{r}
(faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
     theme_few(base_size=16) +
  xlab('Age bin (months)') +
  ylim(0,.5) +
  theme(legend.position="none"))
```

### Plot hands x age x child
```{r}
(hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
     theme_few(base_size=16) +
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5)+
  theme(legend.position="none"))
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  theme_few(base_size=16) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)')+
  theme(legend.position="right"))
```

### Compiled plot
```{r}

ggarrange(faces,hands,face_v_hand, nrow=1)
```

@@

### Plot Face AND hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  ylab('Proportion Face AND Hand') + 
  xlab('Age bin')
```
## By location
### Summarize faces vs hands by location

```{r}

@@

# Cropped analysis

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_cropped$age_days)
max_age = max(d_cropped$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d_cropped <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_cropped$age_day_bin = as.numeric(as.character(d_cropped$age_day_bin))

d_cropped$face_openpose = as.logical(d_cropped$face_openpose)
# d_cropped$hand_openpose = as.logical(d_cropped$hand_openpose)

## Faces vs hands
### Summary statistics
```{r}
summary_by_age_cropped <- d_cropped %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
# 
# summary_by_age_cropped_limited <- summary_by_age_cropped %>%
#   filter(age_day_bin < 24.1)
```

### 2020-01-24 analysis/analysis_goldset.Rmd
separate out analysis scripts for efficiency

## preprocess such that each frame has a true/false value for whether there was a child or adult hand
child_adult_hand_annotations <- g_seg %>%
    mutate(child_hands = (label=="Child hand"), adult_hands = (label=="Adult hand")) %>%
    select(-vid_name) %>%
    rename(vid_name = vid_name_short) %>%
    group_by(full_image_path, vid_name, frame_ind) %>%
    summarize(child_hand_seg = (sum(child_hands))>0,  adult_hand_seg = (sum(adult_hands)>0)) %>%
    mutate(frame = frame_ind) %>%
    select(child_hand_seg, adult_hand_seg, full_image_path, vid_name, frame) 
```

@@

### Hands vs. faces in manual annotations, broken down by child vs. adult hands
```{r}
face_vs_hands_goldset <- d %>%
  full_join(child_adult_hand_annotations, by=c("vid_name", "frame")) %>%
  mutate(frame_id = paste0(vid_name, '-', frame)) %>%
  replace_na(list(adult_hand_seg = FALSE, child_hand_seg = FALSE)) %>% ## replace NAs from segmentation with false for hands since all we got annotations for all frames with hands 
  group_by(child_id, age_day_bin) %>%
  summarize(num_detect = length(unique(frame_id)), prop_faces = sum(face_present_ketan) / num_detect, prop_hands = sum(hand_present_ketan) / num_detect, prop_adult_hands = sum(adult_hand_seg) / num_detect, prop_child_hands = sum(child_hand_seg) / num_detect) %>%
  filter(num_detect > 50) %>% ## need at least x samples per point
  mutate(faces_vs_hands = prop_faces - prop_hands, faces_vs_adult_hands = prop_faces - prop_adult_hands, faces_vs_child_hands = prop_faces - prop_child_hands)  %>%
  filter(!is.na(child_id))

@@

@@

### Code ot render out bounding boxes from OP on sample frames
```{r}
# g_seg_info <- g_seg %>%
#   distinct(full_image_path, vid_name_short, frame_ind)
#   
# bb_check <- bb %>%
#   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
#   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
#   filter(!is.na(full_image_path)) %>%
#   filter(mean_conf > 0)

# # dir.create(paste0('bbcheck/'))
# unique_images <- bb_check$full_image_path[101:200]
# 
# for (image in unique_images){
#   this_image_rgb <- image_read(image)
#   img <- image_draw(this_image_rgb)
#   a <- bb_check %>%
#     filter(full_image_path %in% image) 
#   
#   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
#   text(a$center_x, a$center_y, a$center_y)
#   
#   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
#   image_write(img, annotated_file)
#   dev.off()
# }
```

@@

@@

adult_hands <- g_seg %>%
  filter(label=="Adult hand")
##
ggplot(child_hands, aes(x=left, y=top)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('Child hands (mturk)') +
  ylim(0,height_px) +
  scale_y_reverse()
##
ggplot(adult_hands, aes(x=left, y=top)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ylim(0,height_px) +
  scale_y_reverse() +
  ggtitle('Adult hands (mturk)')

>>>>

## preprocess such that each frame has a true/false value for whether there was a child or adult hand
child_adult_hand_annotations <- g_seg %>%
    mutate(child_hands = (label=="Child hand"), adult_hands = (label=="Adult hand")) %>%
    select(-vid_name) %>%
    rename(vid_name = vid_name_short) %>%
    group_by(full_image_path, vid_name, frame_ind) %>%
    summarize(child_hand_seg = (sum(child_hands))>0,  adult_hand_seg = (sum(adult_hands)>0)) %>%
    mutate(frame = frame_ind) %>%
    select(child_hand_seg, adult_hand_seg, full_image_path, vid_name, frame)

# save(child_adult_hand_annotations, file="../data/child_adult_hand_annotations.RData")
```

@@

### Hands vs. faces in manual annotations, broken down by child vs. adult hands
```{r}
d_with_child_hands <- d %>%
  full_join(child_adult_hand_annotations, by=c("vid_name", "frame")) %>%
  mutate(frame_id = paste0(vid_name, '-', frame)) %>%
  replace_na(list(adult_hand_seg = FALSE, child_hand_seg = FALSE)) ## replace NAs from segmentation with false for hands since all we got annotations for all frames with hands

face_vs_hands_goldset <- d_with_child_hands
  group_by(child_id, age_day_bin) %>%
  summarize(num_detect = length(unique(frame_id)), prop_faces = sum(face_present_ketan) / num_detect, prop_hands = sum(hand_present_ketan) / num_detect, prop_adult_hands = sum(adult_hand_seg) / num_detect, prop_child_hands = sum(child_hand_seg) / num_detect) %>%
  filter(num_detect > 50) %>% ## need at least x samples per point
  mutate(faces_vs_hands = prop_faces - prop_hands, faces_vs_adult_hands = prop_faces - prop_adult_hands, faces_vs_child_hands = prop_faces - prop_child_hands)  %>%
  filter(!is.na(child_id))

```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

bin_size = 30
min_age = min(d_with_child_hands$age_days, na.rm=TRUE)
max_age = max(d_with_child_hands$age_days,na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
d_with_child_hands <- d_with_child_hands %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

prf_by_age_child_hands <- d_with_child_hands %>%
  filter(!is.na(hand_openpose)) %>%
  mutate(child_hand_eval = evaluate_detector(child_hand_seg, hand_openpose)) %>%
  mutate(adult_hand_eval = evaluate_detector(adult_hand_seg, hand_openpose)) %>%
  group_by(age_day_bin, child_id) %>%
  do(return_prf(.$child_hand_eval))

prf_by_age_adult_hands <- d_with_child_hands %>%
  filter(!is.na(hand_openpose)) %>%
  mutate(adult_hand_eval = evaluate_detector(adult_hand_seg, hand_openpose)) %>%
  group_by(age_day_bin, child_id) %>%
  do(return_prf(.$adult_hand_eval))

prf_by_age_child_hands$age_day_bin = as.numeric(prf_by_age_child_hands$age_day_bin)
prf_by_age_adult_hands$age_day_bin = as.numeric(prf_by_age_adult_hands$age_day_bin)

child_hand_scores  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylim(0,.6) +
  ylab('F-score - Child hand detection')

adult_hand_scores = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylab('F-score - Adult hand detection')
  ylim(0,.6) +
ggarrange(child_hand_scores,adult_hand_scores, nrow=1)

  child_hand_scores  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylim(0,.6) +
  ylab('F-score - Child hand detection')

adult_hand_scores = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylab('F-score - Adult hand detection')
  ylim(0,.6) +
ggarrange(child_hand_scores,adult_hand_scores, nrow=1)

  child_hand_scores_r  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylim(0,.6) +
  ylab('Recall - Child hand detection')

adult_hand_scores_r = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylab('Recall - Adult hand detection')
  ylim(0,.6) +
ggarrange(child_hand_scores_r,adult_hand_scores_r, nrow=1)

    child_hand_scores_r  = ggplot(prf_by_age_child_hands, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylim(0,.6) +
  ylab('Precision - Child hand detection')

adult_hand_scores_r = ggplot(prf_by_age_adult_hands, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10)  +
  ylab('Precision - Adult hand detection')
  ylim(0,.6) +
ggarrange(child_hand_scores_r,adult_hand_scores_r, nrow=1)

@@

```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

@@

### Code ot render out bounding boxes from OP on sample frames
```{r}
# # g_seg_info <- g_seg %>%
# #   distinct(full_image_path, vid_name_short, frame_ind)
# #   
# # bb_check <- bb %>%
# #   mutate(frame_ind = frame, vid_name_short = vid_name) %>%
# #   left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
# #   filter(!is.na(full_image_path)) %>%
# #   filter(mean_conf > 0)
# 
# # # dir.create(paste0('bbcheck/'))
# # unique_images <- bb_check$full_image_path[101:200]
# # 
# # for (image in unique_images){
# #   this_image_rgb <- image_read(image)
# #   img <- image_draw(this_image_rgb)
# #   a <- bb_check %>%
# #     filter(full_image_path %in% image) 
# #   
# #   # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)
# #   text(a$center_x, a$center_y, a$center_y)
# #   
# #   annotated_file = paste0('bbcheck/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
# #   image_write(img, annotated_file)
# #   dev.off()
# # }
```

@@

turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID) %>%
  mutate(center_x = left + width/2, center_y = top + height/2)

@@

adult_hands <- g_seg %>%
  filter(label=="Adult hand")

##
child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ggtitle('(A). Child hand density') +
  ylim(0,480) +
  xlim(0,640) +
  theme(legend.position="none") +
  scale_y_reverse()
##
adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ylim(0,480) +
  xlim(0,640) +
  scale_y_reverse() +
  theme(legend.position="none") +
  ggtitle('(B). Adult hand density')

ggarrange(child_hand_plot, adult_hand_plot, nrow=1)

### 2020-01-24 analysis/preprocess_datasets.Rmd
updates to main analysis; first pass at integrating in paper.rmd
separate out analysis scripts for efficiency

@@

# join with metadata and exclude bad videos
d_all <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_all %>%
  filter(!vid_name %in% right_side_up$video)

d_all <- d_all %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_all$vid_name))
assert_that(num_videos_retained < num_orig_videos)

@@

### Make detections into logical vectors and compute "person" as either face/hand
```{r}
d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
```

### Look at any suspicious videos with very high face detections (candidate missed allocentric videos)
```{r}
vid_check <- d_all %>%
  filter(child_id == "S") %>%
  group_by(vid_name,vid_name, Databrary.Link) %>%
  summarize(prop_faces =mean(face_openpose))

high_faces <- vid_check %>%
  filter(prop_faces>.8)
```

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

### And save out into dataframe
```{r}
d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))
```

### Save this data so this doesn't have to be redone again
```{r}
save(d_all, file = '../data/openpose_detections_filtered.RData')
```

## Load bounding boxes to get cropped detections
```{r}
## import bounding boxes
load('../data/all_bounding_boxes.RData')

@@

bb_all <- df %>%
  filter(right_side_up==0) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

@@

## Make cropped detections in top 60% of frame
```{R}
detections_cropped <- bb_all %>%
  filter(height <.6) %>%  ## cut off bottom part of frame
  group_by(vid_name, frame, child_id, age_day_bin) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0)) %>% # if any faces or hands
  distinct(vid_name, frame, age_day_bin,face_detected, hand_detected)

## clean up so that we can join with original dataframe
detections_cropped <- detections_cropped %>%
  ungroup() %>%
  rename(hand_detected_cropped = hand_detected, face_detected_cropped = face_detected) %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))

## now join with big dataframe
d_cropped <- d_all %>%
  as_tibble() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id),face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  select(vid_name, frame, child_id, age_day_bin, face_openpose, hand_openpose) %>%
  left_join(detections_cropped, by=c("vid_name","frame","age_day_bin","child_id"))

d_cropped <- d_cropped %>%
  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE))  ## replace NAs from cropped anlaysis

# and save it out
save(d_cropped, file = '../data/openpose_detections_filtered_cropped.RData')
```

# Render out images based on annotations if desired
## True positives on faces?
```{r eval=FALSE}
faces_only_op_cor <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_tp/'))
for (i in seq(1,length(faces_only_op_cor$full_image_path),1)){
  image_read(as.character(faces_only_op_cor$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_tp/", faces_only_op_cor$short_image_path[i])))
}

@@

## False positives on facs?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == FALSE) %>%
  filter(face_openpose == TRUE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fp/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fp/", to_write$short_image_path[i])))
}

@@

## False negatives on faces?
```{r eval=FALSE}
to_write <- m %>%
  filter(faces == TRUE) %>%
  filter(face_openpose == FALSE)

# how about images where open pose got it? these should be most obvious
dir.create(paste0('faces_fn/'))
for (i in seq(1,length(to_write$full_image_path),1)){
  image_read(as.character(to_write$full_image_path[i])) %>%
  image_append(stack = FALSE) %>%
  image_write(file.path(paste0("faces_fn/", to_write$short_image_path[i])))
}

@@

>>>>

save(meta, file = '../data/saycam_metadata.RData')

@@

# join with metadata and exclude bad videos
d_SA <- detections %>%
  left_join(meta, by='vid_name') %>%
  filter(!vid_name %in% flipped_videos$vid_name)

## All 6 of the video that were not in this file (but were in the detections file) happened to be 6 very bad quality videos; excluding from detections
exclude_bad_quality <- d_SA %>%
  filter(!vid_name %in% right_side_up$video)

d_SA <- d_SA %>%
  filter(!vid_name %in% exclude_bad_quality$vid_name)

# check that we actually excluded the videos
num_orig_videos = length(unique(detections$vid_name))
num_videos_retained = length(unique(d_SA$vid_name))
assert_that(num_videos_retained < num_orig_videos)

@@

## Load, process, merge Y's data
### Now load in bounding box data from Y, which has detection rates built in
```{r}
load('../data/Y_bounding_boxes.RData') #df again
y_data <- df %>%
  rowwise() %>%
  mutate(age = str_split_fixed(vid_name, '_',4)[,3])

remove(df)

### wrangle age data for Y
d_y <- y_data %>%
  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
  mutate(age_days = age_months*30 + days_to_add)

save(y_data, file = '../data/Y_bounding_boxes_cleaned.RData')
```

### Do basic preprocessing on Y detection's
```{r}

### count hands/faces from bounding box outputs for Y -- for d_all
y_detections <- d_y %>%
  group_by(vid_name, frame,age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0))

y_detections <- y_detections %>%
  # rename(hand_openpose = hand_detected, face_openpose = face_detected) %>%
  mutate(child_id = "Y") %>%
  left_join(meta)

save(y_detections, file='../data/y_detections_preprocessed.RData')
```

### Merge detections from Y with other kids
```{r}
d_all <- d_SA %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  full_join(y_detections)
```

### Save this data so this doesn't have to be redone again
```{r}
save(d_all, file = '../data/openpose_detections_filtered_threekids.RData')
```
## Save out vid info for use with joining stuff later
```{r}
# vid_info_all <- d_all %>%
#   select(vid_name, frame, age_days, child_id)
# 
# save(vid_info_all, '../data/vid_info_all.RData')
```
### Look at any suspicious Sam videos with very high face detections (candidate missed allocentric videos)
```{r eval=FALSE}
# vid_check <- d_all %>%
#   filter(child_id == "S") %>%
#   group_by(vid_name,vid_name, Databrary.Link) %>%
#   summarize(prop_faces =mean(face_openpose))
# 
# high_faces <- vid_check %>%
#   filter(prop_faces>.8)
```

# Cropped detections
## Load bounding boxes from S/A to get cropped detections
```{r}
## import bounding boxes
load('../data/all_bounding_boxes.RData')

@@

bb_all <- df %>%
  filter(right_side_up==0)

@@

## Make cropped detections in top 60% of frame for Y
```{r}
load(file = '../data/Y_bounding_boxes_cleaned.RData')
d_y <- y_data %>%
  mutate(age_months = as.numeric(substr(age, 0,2)), days_to_add = as.numeric(substr(age, 3,4))) %>%
  mutate(age_days = age_months*30 + days_to_add)

detections_cropped_Y <- d_y %>%
  filter(person==0) %>% #only get frames where detections
  filter(height <(.6*480)) %>%  ## cut off bottom part of frame
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

detections_cropped_Y <- detections_cropped_Y %>%
 ungroup() %>%
 mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))

@@

## Make cropped detections in top 60% of frame for S,A
```{R}
detections_cropped_SA <- bb_all %>%
  filter(height <.6) %>%  ## cut off bottom part of frame
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected_cropped = (sum(label=="hand")>0), face_detected_cropped = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

all_cropped_detections <- detections_cropped_SA %>%
  ungroup() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  full_join(detections_cropped_Y)

@@

## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in
```{r}
# load('../data/openpose_detections_filtered_threekids.RData') # d_all

d_cropped <- d_all %>% ## needs to be loaded
  as_tibble() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  select(vid_name, frame, child_id, age_days, face_openpose) %>%
  left_join(all_cropped_detections, by=c("vid_name","frame","age_days","child_id")) %>%
  replace_na(list(hand_detected_cropped = FALSE, face_detected_cropped = FALSE ))
```

### now save
```{r}
save(d_cropped, file = '../data/openpose_detections_filtered_cropped_allthreekids.RData')

@@

# Make bb detections only
```{r}
## import bounding boxes
load('../data/all_bounding_boxes.RData')
load('../data/Y_bounding_boxes_cleaned.RData')

right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)

```{r}
## frame
height_px = 480; width_px = 640
bb_all <- y_data %>%
  filter(person==0) %>% # only rows with detections for now
  filter(!is.na(child_id)) %>%
  mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data...
  full_join(df) %>% # join with S/A
  filter(right_side_up==0) %>% # get rid of allocentric
  mutate(center_x = left + width/2, center_y = top - height/2, area = width*height)

save(bb_all, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
